---
title: "Report Template"
author: "Natalie Pottschmidt"
date: "`r Sys.time()`"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
source("mcSummary_function.R")
```

**What did I learn from creating this R markdown template? I haven't done much with Rmd before, so...**
   
- Text formatting
    - Headers
    - Lists
    - Italics, bold, etc. 
- Different options for showing/hiding code and output
- Table of contents in HTML output
- Including R code snippets within text

**How would these features be useful?**
   
I'm planning to use Rmarkdown to create a presentation about my Master's research project proposal to give to my labmates/mentor -- the formatting will be really great for readable slides, and I'll be able to import my data/provide summary statistics/etc. all by knitting one document, rather than copy&pasting! 

# Background
<!-- Give a bit of an exposition to the project, can omit for more technical reports -->

## Topic 1
- Point
    - Evidence
    - Evidence
- Point
    - Evidence
    - Evidence

## Topic 2
- Point
    - Evidence
    - Evidence
- Point
    - Evidence
    - Evidence
    
# Current Study Proposal

## Key Observation
The driving force behind this study; what is the overall motivating observation or question?

## Possible Explanations
<!-- (Optional) -->
Ways that the observation might be explained, or the current state of the literature on the question (e.g. are there divides, etc.)

## Research Questions
1. Question/hypothesis 1
2. Question/hypothesis 2
3. Question/hypothesis 3

# Method

## Procedure
Include study design steps here

## Inclusion/Exclusion Criteria
Explicate criteria

<!-- Data Cleaning Code insert, or source R script -->
```{r Data Cleaning, echo=TRUE}
# load("your_data_here.rda")
# source("your_data_cleaning_script_here.R")
```

<!-- For an example dataset -->
```{r Fake Data, echo=TRUE}
id <- 1:20
sex <- as.factor(rep(c("female","male"), each = 10))
age <- rep(c(21:25), 4)
group <- rep(c(0,1), 10)

set.seed(1215)
var1 <- sample(1:10, 20, replace=T)
var2 <- sample(25:87, 20, replace=T)

YOURDATA <- as.data.frame(cbind(id, group, sex, age, var1, var2))
YOURDATA$group <- factor(YOURDATA$group, levels = c(0, 1), labels = c(1, 2))
YOURDATA$sex <- factor(YOURDATA$sex, levels = c(1, 2), labels = c("female", "male"))

head(YOURDATA)
```

<!-- If you loaded your own data, replace YOURDATA with the name of your actual dataframe -->

## Summary/demographic statistics of sample
Include code output for overall sample stats (N, mean age, gender breakdown, etc.)

- The sample includes **`r nrow(YOURDATA)`** subjects
    - **`r sum(YOURDATA$sex == "female")` (`r round(((sum(YOURDATA$sex == "female"))/nrow(YOURDATA)),2)*100`%)** of these are female
    - average age is **`r mean(YOURDATA$age)` [`r sd(YOURDATA$age)`]**

## Measures
- Measure A
    - Features
- Measure B
    - Features

### Defining items, subscales, groups for analysis
Whatever specific variables, group divisions, etc. will be used in the analyses in the next section

## Group comparison table
```{r Group Table, echo=FALSE, message=FALSE, warning=FALSE}
library(tables)
table <- tabular((group + 1) ~ (n = 1) + sex +
                   Format(digits = 2)*(age + var1 + var2)*(mean + sd), 
                 data=YOURDATA)
table
```

*At this point I wanted to make the table prettier, but using functions like `latex()` or `html()` just printed the table code rather than the pretty table. I couldn't figure out how to make it work.*

## Analyses
```{r Analysis 1, echo=FALSE, message=FALSE, warning=FALSE}
## Example analysis
asscn <- lm(var2 ~ var1, data = YOURDATA)
mcSummary(asscn)

ggplot(YOURDATA, aes(x=var1, y=var2)) + 
  geom_point() +
  geom_smooth(method="lm")

```

```{r Analysis 2, echo=FALSE, message=FALSE, warning=FALSE}

```

```{r Analysis 3, echo=FALSE, message=FALSE, warning=FALSE}

```


# Results

## Analysis 1
Results summary from analysis above.

## Analysis 2
Results summary from analysis above.

## Analysis 3
Results summary from analysis above.

# Discussion
Summarize findings

## Implications
What could the findings mean?

## Strengths & Limitations
What was great about the study?

What could have been better about the study?

